`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!--
If you feel it necessary to include an appendix, it goes here.
-->


# ICD-11 Condition Codes

## Severe Mental Illness Codes

Severe mental illness ICD-11 codes are below.

```{r, echo=FALSE}
library(tidyverse)
library(kableExtra)

table1 <- tibble(
  code = c(
    "6A20",
    "6A21",
    "6A22",
    "6A23",
    "6A24",
    "6A25",
    "6E61",
    "6A2Y",
    "6A2Z",
    "6D10",
    "6D11",
    "6E68",
    "6B40",
    "6B41",
    "6B80",
    "6B81",
    "6B82"
  ),
  diagx = c(
    "Schizophrenia",
    "Schizoaffective disorder",
    "Schizotypal disorder",
    "Acute and transient psychotic disorder",
    "Delusional disorder",
    "Symptomatic manifestations of primary psychotic disorders",
    "Secondary psychotic syndrome",
    "Other specified primary psychotic disorder",
    "Schizophrenia or other primary psychotic disorders, unspecified",
    "Personality disorder",
    "Prominent personality traits or patterns",
    "Secondary personality change",
    "Post traumatic stress disorder",
    "Complex post traumatic stress disorder",
    "Anorexia Nervosa",
    "Bulimia Nervosa",
    "Binge Eating Disorder"
  )
) %>%
  arrange(diagx) # order alphabetically
table1 <- unique(table1) # remove duplicates

# \newpage

## Step 2 - make a \LaTeX table using `kable` {-}

knitr::kable(table1,
  longtable = T, booktabs = T, format = "latex", escape = F,
  row.names = F,
  col.names = c("Code", "Condition")
) %>%
  kable_styling(
    latex_options = c("HOLD_position", "repeat_header"),
    position = "center"
  )
```

## Commom Mental Health Disorder Codes

Common mental heath disoders by ICD-11 code are below.

```{r, echo=FALSE}
library(tidyverse)
library(kableExtra)

table2 <- tibble(
  code = c(
    "6A70",
    "6A71",
    "6A72",
    "6A7Y",
    "6B00",
    "6B01",
    "6B03",
    "6B04",
    "6B05",
    "6B0Y",
    "6B20",
    "6B21",
    "6B23",
    "6B24",
    "6B25",
    "6B25.0",
    "6B25.1",
    "6B2Y"
  ),
  diagx = c(
    "Single Episode Depressive Disorder",
    "Recurrent Depressive Disorder",
    "Dysthymic Disorder",
    "Other Specified Depressive Disorders",
    "Generalized Anxiety Disorder",
    "Panic Disorder",
    "Specific Phobia",
    "Social Anxiety Disorder",
    "Separation Anxiety Disorder",
    "Other Specified Anxiety or Fear-Related Disorders",
    "Obsessive-Compulsive Disorder",
    "Body Dysmorphic Disorder",
    "Hypochondriasis (Health Anxiety Disorder)",
    "Hoarding Disorder",
    "Body-Focused Repetitive Behaviour Disorders",
    "Trichotillomania (Hair Pulling Disorder)",
    "Excoriation (Skin Picking) Disorder",
    "Other Specified Obsessive-Compulsive or Related Disorders"
  )
) %>%
  arrange(diagx) # order alphabetically
table2 <- unique(table2) # remove duplicates

# \newpage

## Step 2 - make a \LaTeX table using `kable` {-}

knitr::kable(table2,
  longtable = T, booktabs = T, format = "latex", escape = F,
  row.names = F,
  col.names = c("Code", "Condition")
) %>%
  kable_styling(
    latex_options = c("HOLD_position", "repeat_header"),
    position = "center"
  )
```


# Code and Analysis

## Accessing the Analysis Code

All analysis code can be accessed via the dedicated GitHub repository:

> [github.com/themichjam/apms_analysis_phd](https://github.com/themichjam/apms_analysis_phd)

## Packages Used

Packages used can be seen here. 

```{r pckgs used, echo = T, results = 'hide', warning = F, message = F}

# if needed
if (!require(pacman)) {
  install.packages("pacman")
  library(pacman)
}
p_load(
  apyramid, # population pyramids aggregated by age
  collapse, # C/C++ based package for advanced data transformation and
  # statistical computing
  DataExplorer, # automated data exploration process for analytic
  # tasks and predictive modeling
  dataReporter, # generates a custom data report with a
  # thorough summary of the checks
  ggpubr, # creating publication ready plots
  ggstats, # suite of functions to plot regression model coefficients
  gt, # presentation ready tables
  gtExtras, # extend gt
  gtsummary, # publication-ready analytical and summary tables
  haven, # read and write various data formats used by
  # other statistical packages
  here, # constructs paths to project's files
  janitor, # examines and cleans dirty data
  jtools, # a collection of tools for more efficiently
  # understanding and sharing the results of
  # (primarily) regression analyses.
  knitr, # facilitate complex data transformation
  marginaleffects, # Compute and plot adjusted predictions,
  # contrasts, marginal effects, and marginal means
  margins, # R port of Stata's 'margins' command
  MetBrewer, # colour palettes of the met gallery
  modelsummary, # publication ready model summaries
  naniar, # allows missing data dependencies to be explored with
  # minimal deviation
  pacman, # conveniently wraps library and package related functions
  patchwork, # plot composer
  performance, # Utilities for computing measures to assess
  # model quality
  psych, # general purpose toolbox for personality, psychometric theory
  questionr, # make the processing and analysis of surveys easier
  readxl, # read in excel files
  report, # produces reports of models and data frames according to
  # best practices
  reprex, # sharing of small, reproducible, and runnable examples
  skimr, # simple to use summary function that can be used with pipes
  srvyr, # 'dplyr' tidy-like syntax for summary statistics
  # of survey data
  # formatting intent
  summarytools, # data frame summaries etc.
  survey, # analysing data from complex surveys
  surveyCV, # K-fold cross validation on complex surveys
  tidymodels, # tidy modelling "verse" of packages for
  # modelling and statistical analysis
  tidyverse, # opinionated collection of R packages designed
  # for data science
  vip, # variable importance plots from models
)
```

## Regression Code

Code for the regression model sets can be seen here.

```{r models, eval=FALSE}

# Model for economic activity in the 2000 survey wave
mod_econ_act_00 <- svyglm(
  econ_act ~ # DV measuring economic activity
    gender + # IV gender
    age_col + # IV collapsed age group
    ethnic_col + # IV collapsed ethnicity
    sc_col + # IV collapsed social class
    edqual_col + # IV collapsed education
    phys_health + # IV derived presence of physical condition
    cmd_pres + # IV derived presence of CMD
    smi_comp, # IV derived presence of SMI comparable
  # to 2007 survey wave
  design = weighted_00, # takes into account weighted
  # complex survey object
  family = binomial # logistic regression
)
# Model for economic activity in the 2007 survey wave
mod_econ_act_07 <- svyglm(
  econ_act ~
    gender +
    age_col +
    ethnic_col +
    sc_col +
    edqual_col +
    phys_health +
    cmd_pres +
    smi_comp,
  design = weighted_07,
  family = binomial
)

# Model for employment status of those indicated as economically
# active only in the 2000 survey wave
mod_emp_stat_00 <- svyglm(
  emp_act_status ~ # DV measuring employment status
    gender + # IV gender
    age_col + # IV collapsed age groups
    ethnic_col + # IV collapsed ethnicity
    sc_col + # IV collapsed social class
    edqual_col + # IV collapsed education
    phys_health + # IV derived presence of a physical condition
    cmd_pres + # IV derived presence of CMD
    smi_comp, # IV derived presence of SMI comparable
  # to 2007 survey wave
  design = weighted_00, # takes into account weighted
  # complex survey object
  family = binomial # logistic regression
)
# Model for employment status of those indicated as economically
# active only in the 2007 survey wave
mod_emp_stat_07 <- svyglm(
  emp_act_status ~
    gender +
    age_col +
    ethnic_col +
    sc_col +
    edqual_col +
    phys_health +
    cmd_pres +
    smi_comp,
  design = weighted_07,
  family = binomial
)

# Model for economic activity in the 2000 survey wave focusing on
# the presence of CMD
mod_cmd_00 <- svyglm(
  econ_act ~ # DV measuring economic activity
    cmd_pres + # IV derived presence of CMD
    gender + # IV gender
    age_col + # IV collapsed age group
    ethnic_col + # IV collapsed ethnicity
    sc_col + # IV collapsed social class
    edqual_col + # IV collapsed education
    phys_health + # IV derived presence of physical condition
    trtment + # IV derived indication of having treatment
    anyhlca, # IV derived indication of using mental health services
  design = weighted_00, # takes into account weighted
  # complex survey object
  family = binomial # logistic regression
)
# Model for economic activity in the 2007 survey wave focusing on the
# presence of CMD
mod_cmd_07 <- svyglm(
  econ_act ~
    cmd_pres +
    gender +
    age_col +
    ethnic_col +
    sc_col +
    edqual_col +
    phys_health +
    trtment +
    anyhlca,
  design = weighted_07,
  family = binomial
)

# Model for economic activity in the 2000 survey wave
# focusing on type of CMD
mod_cmdt_00 <- svyglm(
  econ_act ~ # DV measuring economic activity
    cmd_type + # IV derived indication of type of CMD
    gender + # IV gender
    age_col + # IV collapsed age group
    ethnic_col + # IV collapsed ethnicity
    sc_col + # IV collapsed social class
    edqual_col + # IV collapsed education
    phys_health, # IV derived presence of physical condition
  design = weighted_00, # takes into account weighted
  # complex survey object
  family = binomial # logistic regression
)
# Model for economic activity in the 2007 survey wave
# focusing on type of CMD
mod_cmdt_07 <- svyglm(
  econ_act ~
    cmd_type +
    gender +
    age_col +
    ethnic_col +
    sc_col +
    edqual_col +
    phys_health,
  design = weighted_07,
  family = binomial
)

# Model for economic activity in the 2000 survey wave
# focusing on the presence of SMI
mod_smi_00 <- svyglm(
  econ_act ~ # DV measuring economic activity
    smi_comp + # IV derived presence of SMI comparable
    # to 2007 survey wave
    gender + # IV gender
    age_col + # IV collapsed age group
    ethnic_col + # IV collapsed ethnicity
    sc_col + # IV collapsed social class
    edqual_col + # IV collapsed education
    phys_health + # IV derived presence of physical condition
    trtment + # IV derived indication of having treatment
    anyhlca, # IV derived indication of using mental health services
  design = weighted_00, # takes into account weighted
  # complex survey object
  family = binomial # logistic regression
)
# Model for economic activity in the 2007 survey wave
# focusing on the presence of SMI
mod_smi_07 <- svyglm(
  econ_act ~
    smi_comp +
    gender +
    age_col +
    ethnic_col +
    sc_col +
    edqual_col +
    phys_health +
    trtment +
    anyhlca,
  design = weighted_07,
  family = binomial
)

# Model for economic activity in the 2000 survey wave
# focusing on type of SMI
mod_smit_00 <- svyglm(
  econ_act ~ # DV measuring economic activity
    smi_type + # IV derived indication of type of SMI
    gender + # IV gender
    age_col + # IV collapsed age group
    ethnic_col + # IV collapsed ethnicity
    sc_col + # IV collapsed social class
    edqual_col + # IV collapsed education
    phys_health, # IV derived presence of physical condition
  design = weighted_00, # takes into account weighted
  # complex survey object
  family = binomial # logistic regression
)
# Model for economic activity in the 2007 survey wave
# focusing on type of SMI
mod_smit_07 <- svyglm(
  econ_act ~
    smi_type +
    gender +
    age_col +
    ethnic_col +
    sc_col +
    edqual_col +
    phys_health,
  design = weighted_07,
  family = binomial
)
```


# Reflexivity Promps

More information, including workshop and creative reflexive writing materials can be found on the maintained OSF repository:

> [https://osf.io/h2f4t/](https://osf.io/h2f4t/)

Prompt questions for embedding reflexivity in all stages of the research process are provided here. Note that these prompts may be engaged with on an individual level (i.e., by individual researchers) but can also be beneficial to work through as a research team and sharing as much or as little as any member of the team would feel comfortable with, given the diversity of experiences that members of a collaboration will bring. Making space for honest, structured conversations around positionality within a research team may lead to useful insights. Some of the questions here will have relatively clear-cut answers, whereas others will be more complex and nuanced. For example, the question of identifying as occupying an insider/outsider position is not a clear binary and researchers may align themselves along a spectrum of *“insider/outsider-ness"*.

## Beginner Prompts

These can be split into several research stages. 

### Research Question and Design Stage

Questions:

1. Why do I want to research this group?
2. To what extent am I “within” the participant group that I am researching? Am I an *“insider” or “outsider”* researcher (or do I occupy both positions?)
3. What can I give to this group? Who is represented within the research team?
4. Should I be the one to research this group, or am I taking space away from someone else?

### Data Collection Stage

Questions:

5. Am I intruding on this group? How can I make this as non-coercive as possible?
6. How can I make this research accessible to the population?
7. Do participants understand what their data will be used for?
8. Have I thought beyond traditional ethics? Am I acting ethically?
9. Could my collection methods be problematic?

### Data Analysis and Interpretation Stage

Questions:

10. Am I aware that people have given me this data and that they may not know me (e.g., survey, health, or admin data)?
11. Who are these people behind the data?
12. If I am using existing datasets, are there any silent assumptions in this dataset?
13. Could my analysis of the dataset reproduce existing inequalities?

### Conclusions and Framing Stage

Questions:

14. How does my use of evidence reflect my biases (or the biases of the research team) as researchers and as individuals with their own life, wants, emotions, needs?
15. What do I gain from this research? What does the population I have studied gain?
16. Is there a disconnect between the two questions above? If so, consider the first few questions in this table again.

An indepth discussion can be read at [@RN2410].


# Supplementary Materials 

Supplementary plots and tables can be accessed via the dedicated GitHub repository:

> [github.com/themichjam/apms_analysis_phd](https://github.com/themichjam/apms_analysis_phd)

